\section{Introduction}
Electronic decay processes are initiated by a sub-outer valence ionization
or excitation. The system relaxes by filling the vacancy with an electron and
transferring the excess energy to another electron of the system, which is emitted.
One examples of electronic decay processes is the
well known Auger process. It was first discovered
by Lise Auger-Meitner \cite{Meitner22} and later rediscovered
by Pierre Auger \cite{Auger23}. In order to give credit, where credit is due
\textcolor{blue}
{and following the renaming suggestion of Ref. \cite{renameAuger19},
we will refer to it as the Auger-Meitner process.}
It is found in a variety of different systems like atoms, molecules and solids.
As a consequence, Auger-Meitner spectroscopy
is used for surface analysis in metallurgy,
quality analysis of microelectronics
as well as for basic studies of chemical reaction mechanisms \cite{AES_Seah_86}.
Since the advent of short XUV pulses, it has been a test process for
time-resolved measurements \cite{Smirnova03}
and is often observed as a side product of modern x-ray spectroscopies
\cite{Greczynski20}.
Another relevant and interesting process is the family of Interparticle
Coulombic Decay processes (ICD) \cite{Cederbaum97,Hergenhahn11,Jahnke15}.
A deeper understanding of the effects that determine the decay widths
of electronic decay processes, that
can lead to rule of thumbs, which do not require expensive lifetime
calculations will
be helpful for the interpretation of the observed spectra.
This article aims to provide such a rule of thumb for relative
\textcolor{blue}
{Auger-Meitner}
decay widths
of initial states split by spin-orbit coupling.
In the following, we will assume processes initiated by ionization.

In order to occur, two criteria need to be fulfilled: the energy and the coupling
criterion.
To fulfill the energy criterion the final state energy is required
to be lower than
the energy of the singly ionized initial state. If this is not the case, the
channel defined by a certain doubly ionized final state
is closed and the corresponding fragments of the
channel are not observed after the decay.
To fulfill the coupling criterion, the decay process needs to be fast enough
to prevail over other energetically accessible decay pathways like radiative
relaxation or coupling to nuclear degrees of freedom.
It hence contains
the information whether an energetically allowed process can be expected
to be observed experimentally or not.
Therefore, a typical study of electronic decay processes consists of two parts:
\begin{itemize}
 \item determination of the kinetic energy of the secondary electron
       and, as a consequence, which decay channels are open
 \item calculation of the decay width $\Gamma=\frac{\hbar}{\tau}$, which
       is proportional to the decay rate $\frac{1}{\tau}$ and
       inversely proportional to the lifetime $\tau$
\end{itemize}


The primary ionization often removes an electron from an atomic core, where
relativistic effects are stronger than for valence electrons. The relativistic
effects can therefore be expected to play a crucial role for the understanding
of the systems' lifetimes.
Phenomenologically, the relativistic effects can be divided  
into spin-orbit coupling and scalar-relativistic effects. The spin-orbit       
coupling requires the system to be described in terms of the total angular     
momentum $j$ rather than the orbital momentum $l$ and the spin momentum $s$.   
Thereby the non-relativistically degenerate states of one particular $l$       
value are split into two states with $j=l\pm s$ of different energies          
\cite{ReiherWolf09}.                                            
The scalar-relativistic effects result in spatial contractions of all orbitals on
one-electron systems. In many-electron systems, however, those orbitals with density close
to the nucleus are more strongly contracted than others. They thereby
shield the positive charge of the nucleus from the electrons in other orbitals,
which are therefore effectively spatially decontrated compared to the non-relativistic
solutions. Therefore, as a rule of thumb, $s$ and $p$ are spatially contracted while
$d$ and $f$ orbitals are spatially decontrated. \cite{ReiherWolf09}.

The initial and final state energies can be obtained using      
a variety of quantum chemical approaches known in the literature as the       
Algebraic Diagrammatic Construction \cite{Schirmer82_1,Schirmer91,Schirmer98, 
Mertins96_1} (ADC), which is also                               
available for a fully relativistic treatment                    
\cite{Pernpointner04_1,Pernpointner04_2,Pernpointner10_1}.
The calculation of the respective lifetimes is a challenging task, because it
requires the description of both bound and continuum electrons. The bound electrons
are best described by wavefunctions with $\mathcal{L}^2$ boundary conditions,
while continuum electrons far away from the atom are best described by
plane waves. This imposes the technical choice between a) describing the entire
atom using an $\mathcal{L}^2$ basis, b) describing the entire process using
a grid, or c) describing the bound electrons using an $\mathcal{L}^2$ basis
and the continuum electron using a grid.
Either     
of these approaches faces difficulties in either describing the bound or the  
continuum states or some artificially constructed interface region.
Traditionally, most quantum
chemical program packages are based on $\mathcal{L}^2$ bases and we therefore
choose to describe the electronic decay processes using a large $\mathcal{L}^2$
basis for convenience.

The quantum chemical methods, which have been developed for a relativistic
description of the decay widths are the Multichannel Multi-Configurational
Dirac-Fock (MMCDF) \cite{Fritzsche11} and the FanoADC-Stieltjes \cite{Fasshauer15_1}.
The MMCDF is limited to atomic systems and strongly depends on
the manual selection of CI (Configuration
Interaction) components to be included in the description of initial and      
final states.
The FanoADC-Stieltjes is based on the ADC and not limited to spherically symmetric
systems.
It is furthermore size-consistent and includes terms up to third order
in perturbation theory yielding the interaction between initial and final state
without actually calculating the states themselves.
It is therefore a good compromise between
accuracy and computational cost. At the same time, the configurations needed for the
accurate description of initial and final states are determined automatically up to
the implemented order of the perturbed wavefunction.
The FanoADC-Stieltjes approach is implemented in the relativistic
quantum chemistry package
DIRAC \cite{DIRAC17}, which allows to use different Hamiltonians while keeping
all other parameters constant. This allows us to computationally only consider
scalarrelativistic effects using the spinfree Hamiltonian as well as
performing a fully relativistic calculation using the four-component
Dirac-Coulomb (DC) Hamiltonian taking both scalarrelativistic and
spin-orbit coupling into account.
By comparing the results, we can extract the effect caused by spin-orbit coupling.
We therefore choose the FanoADC-Stieltjes approach for our calculations.


In this work we focus on the atomic Auger-Meitner process     
in order                                      
to exploit basic knowledge about the influence of relativistic effects,
but we expect the conclusions to hold for molecular Auger-Meitner process and
Interparticle Coulombic Decay (ICD) processes
\cite{Cederbaum97,Marburger03,Hergenhahn11,Jahnke15} as well.
The Auger-Meitner decay process initiated by a photoionization
can most generally be described by:
\begin{equation*}                                               
 A \quad \xrightarrow{h\nu}\quad (A^+)^* + e^-_\text{ph} \quad       
    \xrightarrow{\text{Auger-Meitner}} \quad A^{2+} + e^-_\text{ph} + e^-_\text{sec}     
\end{equation*}                                                 
                                                                
A system $A$ is ionized, while the photo-electron $e^-_\text{ph}$ is emitted.      
Afterwards, the actual Auger-Meitner
process of the initial state $A^+$ can occur.    
An electron from an outer                                       
shell fills the vacancy and the excess energy is instantaneously transferred  
to another (secondary) electron $e^-_\text{sec}$, which
is subsequently emitted. The final state of the decay process   
is to be described by a doubly charged atom $A^{2+}$ and the secondary        
electron in the continuum.
\textcolor{blue}
{In the special case when the vacancy filling electron or the secondary
electron stem from an orbital
of the same shell as the initial vacancy the process is called Coster-Kronig decay.
When both are from the same shell, the process is referred to as Super-Coster-Kronig
decay. These Coster-Kronig decays are characterized by very large decay widths.
\cite{Coster35}
}

We have previously shown, how
scalar-relativistic effects influence the decay widths of the Auger-Meitner
process in
noble gas atoms. \cite{Fasshauer15_1}
After primary ionization from the $(n-1)d$ orbitals the nobel
gas atoms decay to $np^{-2}$, $np^{-1}ns^{-1}$ and $ns^{-2}$ final states.
We observed that the Auger-Meitner decay widths increased by up to \unit[326]{\%}
for radon
by including scalar-relativistic effects in the calculation. This
dramatic increase could be explained by the larger spatial
overlap of the orbitals
involved in the decay compared to non-relativistic calculations due to
a contraction of the $s$ and $p$ orbitals of the final states.\\
However, the fully relativistic calculation resulted in different decay widths
for the different $d_{3/2}^{-1}$ and $d_{5/2}^{-1}$ initial states split by
spin-orbit coupling (see Fig.~5 of Ref.~\cite{Fasshauer15_1}).
The aim of this work is therefore to investigate the
influence of spin-orbit coupling on the decay widths of electronic decay processes.
For this purpose, we will study the Auger-Meitner processes of earth alkaline atoms
after primary ionization from the $(n-1)p$ orbitals. The earth alkaline elements
have the benefit of a single and closed shell $ns^{-2}$ final state.
This might allow us to purely observe how the spin-orbit splitting of
the different initial states affects the Auger-Meitner decay width.
\textcolor{blue}
{
Moreover, in the single particle picture, a Coster-Kronig decay is possible for neither
of the initial states and thus the pure Auger-Meitner process, where the initial
states have an equal number of possible decay channels, can be observed.
}
Having only one final state, which is not affected by spin-orbit coupling,
reduces the complexity of the analysis of the results significantly.

The paper is structured as follows:
in section \ref{section:theory} we recapitulate the basics of the
FanoADC-Stieltjes method. We then give the computational details for our
ab initio calculations in section \ref{section:computational}. We present the
results and their interpretation in section \ref{section:results}
and conclude in section \ref{section:conclusions}.
